R Coding Exercise

### 2024-07-10 data-exercise/data-exercise.qmd
online exactly the same as my local
update website for data exercise

---
title: "Date Exercise"
---

Placeholder file for the future data exercise.

```{r}
library(MASS)
library(synthpop)
library(tidyverse)
library(dplyr)
library(writexl)
library(ggplot2)
```

>>>>

---
title: "R Coding Exercise"
---

Placeholder file for data coding exercise.

## Loading and Checking Data
### Import libraries
```{r}
library(MASS)
library(synthpop)
library(tidyverse)
library(dplyr)
library(writexl)
library(ggplot2)
```
